---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading necessary  libraries
I use following lirbraries.  
* dplyr
* lubridate
```{r}
library(dplyr)
library(lubridate)
```


## Loading and preprocessing the data
Loading surce data, and convert 'interval' value to time value.
```{r}
activity_csv <- read.csv(unzip("activity.zip"))
activity_csv <- mutate(activity_csv, time = sprintf("%02d:%02d", interval%/%100, interval%%100))
activity_csv <- mutate(activity_csv, datetime_str = paste(activity_csv$date, " ", activity_csv$time))
activity_csv <- mutate(activity_csv, 
                       datetime = as.POSIXct(strptime(activity_csv$datetime_str, "%Y-%m-%d %H:%M")))
str(activity_csv)
head(activity_csv)
summary(activity_csv)
```


## What is mean total number of steps taken per day?

### Calculate total steps per day.
Calculate total step per day, and show summary informations.
```{r}
# summarise data by day
summarise_data <- group_by(activity_csv, date) %>% summarise(steps = sum(steps, na.rm = TRUE))
str(summarise_data)
summary(summarise_data)
head(summarise_data)
```

### Show histgram of steps/day
Show hishgram of steps/day by plot().
```{r}
hist(summarise_data$steps, 
     breaks = 50,
     xlab = "Toal steps per day", 
     ylab = "Frequency", 
     main = "Histgram of stpes/day")
```

### Calclurate mean and median of total steps/day
Calculate and print mean value and median value of total steps/day.
```{r}
summary(summarise_data$steps)
sprintf("median : %.3f", median(summarise_data$steps))
sprintf("mean   : %.3f", mean(summarise_data$steps))
```


## What is the average daily activity pattern?
### Calculate average value
Calculate average value, grouping by 'interval' column.
And show summary informations.
```{r}
average_daily_data <- group_by(activity_csv, interval, time) %>% summarise(steps = mean(steps, na.rm = TRUE))
str(average_daily_data)
summary(average_daily_data)
head(average_daily_data)
```

### Plot activity pattern
Show line plot by plot().
```{r}
plot(x = average_daily_data$interval, y = average_daily_data$steps,
     type = "l",
     xlab = "the 5-minute interval",
     ylab = "averaged across all days ",
     main = "The average daily activity pattern"
     )
```

Show interval that have maximum steps. 
```{r}
filter(average_daily_data, steps == max(average_daily_data$steps))
```


## Imputing missing values

### Compute missing value's count.
Compute missing value's count.
```{r}
sum(is.na(activity_csv))
```

### Strategy for filling in all of the missing values in the dataset.
I use mean value of all days (expect NA day) for substitution value of missing value.
```{r}
filling_data  <- group_by(activity_csv, date) 
filling_data$steps[is.na(filling_data$steps)] = mean(filling_data$steps, na.rm = TRUE)
summary(filling_data)
```

Show histgram based in filling missing values, and calculate median, mean, differences.
```{r}
summarise_data2 <- group_by(filling_data, date) %>% summarise(steps = sum(steps, na.rm = TRUE))
hist(summarise_data2$steps, 
     breaks = 50,
     xlab = "Toal steps per day", 
     ylab = "Frequency", 
     main = "Histgram of stpes/day")

summary(summarise_data2$steps)
sprintf("median : %.3f", median(summarise_data2$steps))
sprintf("mean   : %.3f", mean(summarise_data2$steps))
sprintf("differ median : %.3f", median(summarise_data2$steps) - median(summarise_data$steps))
sprintf("differ mean   : %.3f", mean(summarise_data2$steps) - mean(summarise_data$steps))
```


## Are there differences in activity patterns between weekdays and weekends?
Create new data.frame that have new  factor variable.
```{r}
activity_csv_w_weekday <- mutate(activity_csv, 
                                 weekdays = factor(if_else(wday(activity_csv$datetime) %in% c(1,7), "weekdays", "weekends")))
average_daily_data2 <- group_by(activity_csv_w_weekday, interval, time, weekdays) %>% summarise(steps = mean(steps, na.rm = TRUE))
str(average_daily_data2)
summary(average_daily_data2)
head(average_daily_data2)
```

Plot line plot weekdays and weekends.
```{r}
step_data_weekdays <- filter(average_daily_data2, weekdays == "weekdays")
step_data_weekends <- filter(average_daily_data2, weekdays == "weekends")
plot(x = step_data_weekdays$interval, y = step_data_weekdays$steps, 
     type = "l",
     xlab = "the 5-minute interval",
     ylab = "averaged across all days ",
     main = "The average daily activity pattern", 
     col = "red",
     ylim = c(0, 300)
     )
par(new = T)
plot(x = step_data_weekends$interval, y = step_data_weekends$steps, 
     type = "l",
     xlab = "the 5-minute interval",
     ylab = "averaged across all days ",
     main = "The average daily activity pattern", 
     col = "blue",
     ylim = c(0, 300)
     )
legend("topleft", legend=c("weekdays", "weekends"), lty=c(1, 1), col=c("red", "blue"))
```